Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-08 appendix.tex
tex
u
lyx

	\item [GA] Re-design Gradual Adversary (Linear Addition)
		\[
			\big(1-\frac{\text{Clip}_0^{U_L}[l_{t-1}]}{U_L} \big)\times U_H
		\]
		Increase $E[H]$ to $E[H]+\alpha U_H$. $E[H]$ is expected to decrease
		with a well-learned model. So without GA, the strength of adversary
		will decrease.

@@

@@

>>>>

	\item [HM] do we fix the anchor like ACT? | marginal. Queued.

@@

	\item [T] Face verification (biometrics) and DML robustness.

	\item [T] Unsup learning with DML robustness.

@@

	\item [\xmark] What if we truncate $H_D$. Clamp it with $\min=-\gamma$.
		| clipping leads to negative effect on fashion-mnist. (ghmetrm 8)

	\item [\xmark] Re-design Gradual Adversary (Linear Addition)
		\[
			\big(1-\frac{\text{Clip}_0^{U_L}[l_{t-1}]}{U_L} \big)\times U_H
		\]
		Increase $E[H]$ to $E[H]+\alpha U_H$. $E[H]$ is expected to decrease
		with a well-learned model. So without GA, the strength of adversary
		will decrease. | Linear GA has a negative effect as observed on
		Fashion-MNIST.
